Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-08-31 paper.tex
no message

%Single insitute
\author{Onur Yılmaz \and Pınar Karagöz}
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{Computer Engineering Department, Middle East Technical University, Turkey}
\email{yilmaz.onur@metu.edu.tr}\and \email{karagoz@ceng.metu.edu.tr}
%Multiple insitutes
%Currently disabled
%
\iffalse
%Multiple institutes are typeset as follows:
\author{Firstname Lastname\inst{1} \and Firstname Lastname\inst{2} }
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blindtext

Winery~\cite{Winery} is graphical modeling tool.

\begin{figure}
Simple Figure
\caption{Simple Figure}
\label{fig:simple}
\end{figure}

\begin{table}
\caption{Simple Table}

\label{tab:simple}
Simple Table
\end{table}

cref Demonstration: Cref at beginning of sentence, cref in all other cases.

\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.

\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.

\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.

Brackets work as designed:
<test>

The symbol for powerset is now correct: $\powerset$ and not a Weierstrass p ($\wp$).

\begin{inparaenum}
\item All these items...
\item ...appear in one line
\item This is enabled by the paralist package.
\end{inparaenum}

``something in quotes'' using plain tex or use \enquote{the enquote command}.

\section{Conclusion and Outlook}

\subsubsection*{Acknowledgments}
...

In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
E.g., \enquote{The 2\textsuperscript{nd} conference on examples}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{splncs03}
\bibliography{paper}

All links were last followed on October 5, 2014.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%Single insitute
\author{Onur Yilmaz \and Pinar Karagoz}
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{Computer Engineering Department, Middle East Technical University, Turkey}
%\email{yilmaz.onur@metu.edu.tr} 
%\email{karagoz@ceng.metu.edu.tr}
%Multiple insitutes
%Currently disabled
%
\iffalse
%Multiple institutes are typeset as follows:
\author{Firstname Lastname\inst{1} \and Firstname Lastname\inst{2} }
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}

@@

\input{1_introduction/introduction.tex}

\bibliographystyle{splncs03}
\bibliography{references/references}
